Title

### 2019-05-22 4_method.tex
enhance transitioning

In order to apply the beading strategy to the MAT, we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
The transition will be placed so as to overlap the locations of $b^{-1}(n)$.
We assign each node $v$ of the medial axis a value $b^*$ which is initially based on $b(R(v))$, but it is modified in order to account for transitioning zones.
On the one side of the transition we will have $b^*(v_0)=\frac12 n$ and on the other side we will have $b^*(v_1)=\frac12 n + \frac12$.
For all locations on the MAT in between we linearly interpolate the $b^*$ values, so that we can later interpolate the bead widths $W$ linearly as well.

In a narrow wedge region (a.k.a. a cusp) we have to transfer from $n$ to $n-1$ beads; this transition requires a distance.
See \cref{single_bead_strategy_overview}.
The transition will be such that the innermost toolpath makes a \SI{45}{\degree} angle with the medial axis.
The length of the transition along the medial axis depends on the angles involved.
See \cref{transition_length}.
\begin{equation}
t = r_0 (\sin \alpha + \cos \alpha)
\end{equation}

@@

The position of the transition is somehwre in between whole tick values.
The relative position in between the whole tick values relates to the relative position of the preferred line width within the range of possible widths.
For a distance $d$ in between a location on the medial axis with a MAT distance of $nr_*$ and one with $(n+1)r_*$ the transition should be positioned around $d - d\frac{r_* - r_-}{r_+ - r_-}$ from the former location.
See \cref{transition_location}.
However, where should the transition be placed precisely? Should the middle of the transition be at that location, or do we again take a relative position of the transition to be at that location?
For extremal values of $r_*$ the transition could overlap with the whole ticks if we simple place the middle of the transition at the specified location.
We therefore place the same ratio of the transition is before the specified location.

\hl{We would like to have a formulation of the MAT distance stransform which defines the MAT distance for any position even if it's not possible to define where the middle of the transition would end up.}
In terms of dMAT/dEuclidean?

The transition needs to be robust against extra fingers in the MAT.
How do we compute the vertex location of an inset on a finger which crosses a transitioning area?
By interpolating the MAT distance between the two ends of the transition, we obtain a stable method for determining the vertex locations of insets.
See \cref{distance_rounding_transition}.
The extra fingers (blue) cause a negligible difference in the inset path (compare the black dashed pat hwith the red dashed path).
\hl{Does this hold for any angled wedge? How about point-line segments or point-point segments?}

@@

\subsubsection{Ends of markings}
There are multiple ways in which a sequence of bones starting from the outline polygon can be said to end.
\begin{enumerate}
\item The last node in the sequence is a local maximum
\item The last node in the sequence is not connected to a marked segment
\end{enumerate}

The tick quantity measure should be rounded
where the MAT distance measure is a local maximum: when all directly connected nodes have a lower MAT distance measure.
See bottom of \cref{rounded_vs_unrounded}.

For vertices at the end of a sequence of marked MAT segments we need to take care of transitions.
If a transition is overlapping the end of the sequence, then either end of the transition would fall beyond the area where transitions should occur.
How should we deal with thse?
\begin{itemize}
\item We need to keep the transition tick on the marked side, because we need to switch to a different number of ticks somewhere.
Moreover, leaving out the whole transition around end-of-markings would violate the stability principle.
\item The end-of-marking itself will retain its interpolated MAT distance as described above.
\item The transition tick on the non-marked side of discarded.
This means that there will also be no single bead segment leading up to the transition, which coincides with how we deal with non-marked areas.
See \cref{single_bead_strategy}.
\end{itemize}
This method of dealing with end-of-markings can result in gaps slightly larger than usual.
See \cref{change_to_marked}.

>>>>

In order to prevent discontinuities in the toolpaths around locations $p$ where $\exists n : R(p) = b^{-1}(n)$ (see \cref{transition_location}), we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
The transition will be placed so as to overlap the locations of $b^{-1}(n)$.

On the one side of the transition we will have $b^*(v_0)=\frac12 n$ and on the other side we will have $b^*(v_1)=\frac12 n + \frac12$.
For all locations on the MAT in between we linearly interpolate the $b^*$ values, so that we can later interpolate the bead widths $W$ linearly as well.

In a narrow wedge region (a.k.a. a cusp) we have to transfer from $n$ to $n+\nicefrac12$ beads; this transition requires a distance.
See \cref{single_bead_strategy_overview}.
The transition will be such that the innermost toolpath makes a \SI{45}{\degree} angle with the medial axis.
The length of the transition along the medial axis depends on the angles involved.
See \cref{transition_length}.
\begin{equation}
t = r_0 (\sin \alpha + \cos \alpha)
\end{equation}

@@

The position of a transition should be at a location $p$ where $\exists n : R(p) = b^{-1}(n)$.
However, given the fact that a transition is a region rather than a point, which part of the transition should be ceneterd at $p$?
For a transition from $n$ to $n+\frac12$ beads, we place a fraction of the transition length toward the end with lower $R$ proportional to it's positioning within the region of non-prefered widths:
$ (b^{-1}(n+\frac12) - p(n) ) / (p(n + \frac12) - p(n))$

\begin{figure}[H]
\centering
\includegraphics[width=.5\columnwidth]{sources/method/transition_location_precise.pdf}
\caption{Transition placement. The anchor position within the transition length is proportional to the transition location within the range between two distances with prefered length. \hl{outdated functions and variables!}}
\label{transition_length}
\end{figure}

\hl{How to deal with non-marked regions shorter than the transition length?}

The transition needs to be robust against extra fingers in the MAT.
How do we compute the vertex location of an inset on a finger which crosses a transitioning area?
By interpolating the MAT distance between the two ends of the transition, we obtain a stable method for determining the vertex locations of insets.
See \cref{distance_rounding_transition}.
The extra fingers (blue) cause a negligible difference in the inset path (compare the black dashed pat hwith the red dashed path).
\hl{What does it look like for point-line segments or point-point segments?}

@@

\subsubsection{Ends of markings}
For vertices at the end of a sequence of marked MAT segments we need to take care of transitions.
If a transition is overlapping the end of the sequence, then either end of the transition would fall beyond the area where transitions should occur.
How should we deal with thse?
\begin{itemize}
\item We need to keep the transition tick on the marked side, because we need to switch to a different number of ticks somewhere.
Moreover, leaving out the whole transition around end-of-markings would violate the stability principle.
\item The end-of-marking itself will retain its interpolated MAT distance as described above.
\item The transition tick on the non-marked side of discarded.
This means that there will also be no single bead segment leading up to the transition, which coincides with how we deal with non-marked areas.
See \cref{single_bead_strategy}.
\end{itemize}
This method of dealing with end-of-markings can result in gaps slightly larger than usual.
See \cref{change_to_marked}.
